The \dealii{} Library, Version 9.3

### 2021-06-17 9.3/paper.tex
updates to sec. 2.7

An internet connection is not necessary for the run, if the source files
are downloaded and repositories are checked out to its unpacking location.
The download of a package can be supported via a local or remote mirror server
similar as we are doing it already for several of the packages.
%
If the temporary files of \candi{} are not removed, one can use a developer
mode to prepare patches or developments for any of the packages.
%
A new feature allows \candi{} to skip user prompts which can be used for
a batch mode run on a compute cluster job for instance.

This source based installer is implemented in a modular fashion. The main
script is implemented without any knowledge on a package or toolchain for
a specific operating system (platform).

The installer is organised in the following way:
\begin{itemize}
\item \texttt{candi.sh}: the bash-script which controls the overall process.

@@

\item \texttt{deal.II-toolchain} folder: the central project folder for
\dealii{}-based toolchains.
It contains subfolders for individual packages, platforms (operating systems)
and for patches to be applied after unpacking a package.

>>>>

An internet connection isn't necessary
if the source files are downloaded and
repositories are checked out to its unpacking location,
e.g. from a previous run on a machine having an internet connection.
%
The download of a package can be supported via local or remote mirror servers
similar as we are doing it already for several of the packages.
%
If the temporary files of \candi{} aren't removed, one can use the developer
mode to prepare patches or developments for any of the packages.
%
A new feature allows \candi{} to skip user prompts which can be used for
a batch mode run on a compute cluster job for instance.

This source based installer is implemented in a modular fashion.
The \texttt{candi.sh} script is implemented without any knowledge
on a package or toolchain for a specific operating system.
Therefore, a couple of checks and setting internal variables
for known platforms are done.

The \candi{} source based installer is organised in the following way:
\begin{itemize}
\item \texttt{candi.sh}: the bash-script which controls the overall process.
The command line options are given by the output of ``\texttt{candi.sh -h}''
and explained in the \texttt{README.md} file.

@@

\item \texttt{deal.II-toolchain} folder: the central project folder for
\dealii{}-based toolchains.
It contains subfolders
for packages (libraries, dependencies, general tools in a specific version),
platforms (operating systems) and
for patches to be applied after unpacking a package.
